Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-28 README.Rmd
formatting changes

[**`code`**](code)

Contains the R code associated with the manuscript that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):

- [`01-raw-file-compression.Rmd`](code/01-raw-file-compression.Rmd)/`.html` contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
- [`02-data-preparation.Rmd`](code/02-data-preparation.Rmd)`/.html` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
- [`03-submission-steps.Rmd`](code/03-submission-steps.Rmd)`/.html` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal

[**`cover-letter`**](cover-letter)

@@

[**`data`**](data/)

@@

- [`bullet-train.csv.zip`](data/bullet-train.csv.zip) and [`bullet-test.csv.zip`](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript. See ""Additional Information on Bullet Data" below for more information about the data.
- [`example-signatures.csv.zip`](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [`raw`](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
  - [`CCFs_withlands.csv.zip`](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [`h224-set1-features.rds.zip`](data/raw/h224-set1-features.rds.zip) and [`h224-set11-features.rds.zip`](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [`signatures.rds.zip`](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [`readme.txt`](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.

[**`figure-static`**](figure-static/)

@@

- [`figure-08-1.png.zip`](figure-static/figure-08-1.png.zip) is the one figure in the manuscript that is not generated using R code.
- [`figure-readme.png`](figure-static/figure-readme.png) is a figure used in this readme.

[**`LEAscans`**](LEAscans/)

@@

[**`old-version`**](old-version/)

@@

[**`submission`**](submission)

Contains the files submitted to the ASA Data Science Journal. These files are moved to this folder using code in the file `code/submission-steps.R`. The only submission files not included on GitHub are the EPS figures due to size constraints.

@@

- [`.gitignore`](.gitignore) contains objects to be ignored by git.
- [`paper.Rnw`](paper.Rnw), [`paper.pdf`](paper.pdf), and [`paper.tex`](paper.tex) are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- [`README.Rmd`](README.Rmd) and [`README.md`](README.md) are the readme files that generated this output.
- [`references.bib`](references.bib) contains the bibtex information for the references in the manuscript.
- [`WileyNJG-AMS.bst`](WileyNJD-AMS.bst) and [`WileyNJG-v2.cls`](WileyNJD-v2.cls) contain the latex formatting specifications for the ASA Data Science Journal.

@@

When the manuscript is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`). The first time the manuscript is knit, it will take a while (possibly up to several hours). Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately a few minutes).

@@

3. Knit manuscript (via the `paper.Rnw` file).

@@

The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file `data/readme.txt` that is submitted with the manuscript.

### `bullet-train.csv`

@@

**bullet-train** is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip). The steps taken to create **bullet-train** from the raw data are found [here](code/02-data-preparation.Rmd). These steps involve renaming some variables, selecting the variables of interest for the manuscript, and adjusting the land IDs associated with the signatures.

@@

- `r names(bullet_train)[1]`: ID number associated with the bullet-land signature comparison.
- `r names(bullet_train)[2]`, `r names(bullet_train)[3]`: IDs describing the two land engraved areas in the comparison. The format is `study-barrelnumber-bulletnumber-landnumber`.

@@

- `r names(bullet_train)[4]`: Maximized cross-correlation between two LEA signatures.
- `r names(bullet_train)[5]`: Correlation after detrending aligned signatures.
- `r names(bullet_train)[6]`: Euclidean distance (in millimeters) between two aligned signatures.
- `r names(bullet_train)[7]`: Standard deviation of the previous measure along the signature.
- `r names(bullet_train)[8]`, `r names(bullet_train)[9]`: Number of matching/non-matching peaks and valleys in the aligned signatures.
- `r names(bullet_train)[10]`: Consecutively matching striae is a measure introduced by @biasotti:1959 describing the longest run of matching peaks between two aligned signatures.
- `r names(bullet_train)[11]`: The number of consecutively non-matching peaks.
- `r names(bullet_train)[12]`: The depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
- `r names(bullet_train)[13]`: Ground truth whether a pair is from the same source (`TRUE`) or from different sources (`FALSE`).

### `bullet-test.csv`

[**bullet-test**](data/bullet-test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets. Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Similar to the training set, each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. **bullet-test** is generated from the raw versions of the data for [set 1](data/raw/h224-set1-features.rds.zip) and [set 11](data/raw/h224-set11-features.rds.zip). The variables in the test data are the same as the training data described above.

### `example-signatures.csv`

@@

- `r names(signatures)[1]`: Indicator variable whether the observation corresponds to "Signature 1" or "Signature 2".
- `r names(signatures)[2]`: The (relative) x position of the signature (in microns).
- `r names(signatures)[3]`: The (relative) y position of the signature height (in microns).

>>>>

[**code**](code)

Contains the R code associated with the manuscript that is not directly included in [paper.Rnw](paper.Rnw) (such as some external data cleaning and file organization):

- [01-raw-file-compression.Rmd](code/01-raw-file-compression.Rmd)/[.html](code/01-raw-file-compression.html) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
- [02-data-preparation.Rmd](code/02-data-preparation.Rmd)/[.html](code/02-data-preparation.html) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
- [03-submission-steps.Rmd](code/03-submission-steps.Rmd)/[.html](code/03-submission-steps.html) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal

[**cover-letter**](cover-letter)

@@

[**data**](data/)

@@

- [bullet-train.csv.zip](data/bullet-train.csv.zip) and [bullet-test.csv.zip](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript. See ""Additional Information on Bullet Data" below for more information about the data.
- [example-signatures.csv.zip](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [raw](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files*:
  - [CCFs_withlands.csv.zip](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [h224-set1-features.rds.zip](data/raw/h224-set1-features.rds.zip) and [h224-set11-features.rds.zip](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [signatures.rds.zip](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [readme.txt](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.

[**figure-static**](figure-static/)

@@

- [figure-08-1.png.zip](figure-static/figure-08-1.png.zip) is the one figure in the manuscript that is not generated using R code.
- [figure-readme.png](figure-static/figure-readme.png) is a figure used in this readme.

[**LEAscans**](LEAscans/)

@@

[**old-version**](old-version/)

@@

[**submission**](submission)

Contains the files submitted to the ASA Data Science Journal. These files are moved to this folder using code in the file [code/03-submission-steps.R](code/03-submission-steps.Rmd). The only submission files not included on GitHub are the EPS figures due to size constraints.

@@

- [.gitignore](.gitignore) contains objects to be ignored by git.
- [paper.Rnw](paper.Rnw), [paper.pdf](paper.pdf), and [paper.tex](paper.tex) are the manuscript. Note that paper.pdf and paper.tex are generated by paper.Rnw.
- [README.Rmd](README.Rmd) and [README.md](README.md) are the readme files that generated this output.
- [references.bib](references.bib) contains the bibtex information for the references in the manuscript.
- [WileyNJG-AMS.bst](WileyNJD-AMS.bst) and [WileyNJG-v2.cls](WileyNJD-v2.cls) contain the latex formatting specifications for the ASA Data Science Journal.

@@

When the manuscript is knit, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png). The first time the manuscript is knit, it will take a while (possibly up to several hours). Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately a few minutes).

@@

3. Knit manuscript (via the [paper.Rnw](paper.Rnw) file).

@@

The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file [data/readme.txt](data/readme.txt) that is submitted with the manuscript.

### bullet-train.csv

@@

bullet-train is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip). The steps taken to create bullet-train from the raw data are found [here](code/02-data-preparation.Rmd). These steps involve renaming some variables, selecting the variables of interest for the manuscript, and adjusting the land IDs associated with the signatures.

@@

- **`r names(bullet_train)[1]`**: ID number associated with the bullet-land signature comparison.
- **`r names(bullet_train)[2]`**, **`r names(bullet_train)[3]`**: IDs describing the two land engraved areas in the comparison. The format is "study-barrelnumber-bulletnumber-landnumber".

@@

- **`r names(bullet_train)[4]`**: Maximized cross-correlation between two LEA signatures.
- **`r names(bullet_train)[5]`**: Correlation after detrending aligned signatures.
- **`r names(bullet_train)[6]`**: Euclidean distance (in millimeters) between two aligned signatures.
- **`r names(bullet_train)[7]`**: Standard deviation of the previous measure along the signature.
- **`r names(bullet_train)[8]`**, **`r names(bullet_train)[9]`**: Number of matching/non-matching peaks and valleys in the aligned signatures.
- **`r names(bullet_train)[10]`**: Consecutively matching striae is a measure introduced by @biasotti:1959 describing the longest run of matching peaks between two aligned signatures.
- **`r names(bullet_train)[11]`**: The number of consecutively non-matching peaks.
- **`r names(bullet_train)[12]`**: The depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
- **`r names(bullet_train)[13]`**: Ground truth whether a pair is from the same source ("TRUE") or from different sources ("FALSE").

### bullet-test.csv

[**bullet-test**](data/bullet-test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets. Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Similar to the training set, each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the bullet-test data. This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. bullet-test is generated from the raw versions of the data for [set 1](data/raw/h224-set1-features.rds.zip) and [set 11](data/raw/h224-set11-features.rds.zip). The variables in the test data are the same as the training data described above.

### example-signatures.csv

@@

- **`r names(signatures)[1]`**: Indicator variable whether the observation corresponds to "Signature 1" or "Signature 2".
- **`r names(signatures)[2]`**: The (relative) x position of the signature (in microns).
- **`r names(signatures)[3]`**: The (relative) y position of the signature height (in microns).
